Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-29 paper.tex
edits

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Enrichment feeds LWRs with fresh
fuel with infinite capacity. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2000 MTHM/yr capacity and increases to 3000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it is
available for separation. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.  Compositions used for the simulations
were simple containing primarily $^{238}U$, $^{235}U$, $^{239}Pu$, $^{241}Am$,
and small quantities of a few lanthanides.  Full composition details can be
found in the Cyclus input files used \cite{Carlsen2015}.

@@

A pre-release of Cyclus version 1.4 was used for this analysis.  Archetypes
used were the standard ones provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage facility was
used because Cycamore did not yet provide one.  The standard cycamore reactor
was used for both LWR and SRF reactor types in cases 1 and 3.  Correspondingly
the custom fleet-based reactor described earlier was used for both reactor
types in cases 2 and 4.  Additional configuration for the reactor types are
shown in Table \ref{tab:reactors}.

@@

The described scenario is used as closely as possible in each of the four
cases.  A few other small case-dependent changes to the scenario relating to
reactor configuration are necessary.  For the cases using quarterly time steps
with individual reactors, cycle and outage times must be adjusted to be a
multiple of 3 months.  In order to make the comparison more fair, the cases
with monthly time steps are also adjusted to have identical cycle and outage
times.  The invariants preserved with respect to reactor behavior between all
four cases are shown in Table \ref{tab:invar}.  Table \ref{tab:reactors} shows
the computed/selected configuration for both LWR and SFR reactor types for all
four cases.

@@

In each of the four cases, the initial 100 LWRs are modified to have a zero
length refueling outage with an explicit 900 MWe power capacity.  This was
done to avoid having all the initial LWRs in the individual reactor cases
refuel at the same time.  The parameters for each case were also selected to
keep capacity factors for individual reactors very roughly around 90\%.

A longer 21-month deployment period is used because it provides better natural
staggering for the reactor refueling cycles. The same deployment schedule is
used for all four cases; power capacity is built along a curve starting at
100GWe in year zero following the 1\% exponential growth curve.  This
particular deployment schedule causes significant fuel shortages providing
interesting features to investigate and compare.

The input files and other assets used in the analysis for each of the four
cases are publicly available for download \cite{Carlsen2015}.

>>>>

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Enrichment feeds LWRs with fresh
fuel with infinite capacity. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2000 MTHM/yr capacity and increases to 3000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it becomes
available for separation. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.  Compositions used for the simulations
were simple containing primarily $^{238}U$, $^{235}U$, $^{239}Pu$, $^{241}Am$,
and small quantities of a few lanthanides.  Full composition details can be
found in the Cyclus input files used \cite{Carlsen2015}.

@@

A pre-release of Cyclus version 1.4 was used for this analysis.  Archetypes
used were the standard ones provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage facility was
used because Cycamore did not yet provide one.  The standard cycamore reactor
was used for both LWR and SRF reactor types in cases 1 and 3.  Correspondingly
the custom fleet-based reactor described earlier was used for both reactor
types in cases 2 and 4.  Additional configuration for the reactor types is
shown in Table \ref{tab:reactors}.

@@

The described scenario is used as closely as possible in each of the four
cases.  However, a few small case-dependent changes to the scenarios relating to
reactor configuration are necessary.  For the cases using quarterly time steps
with individual reactors, cycle and outage times must be adjusted to be a
multiple of 3 months.  In order to make the comparison more fair, the cases
with monthly time steps are also adjusted to have identical cycle and outage
times.  The invariants preserved with respect to reactor behavior between all
four cases are shown in Table \ref{tab:invar}.  Table \ref{tab:reactors} shows
the computed/selected configuration for both LWR and SFR reactor types for all
four cases.

@@

In each of the four cases, the initial 100 LWRs are modified to have a zero
length refueling outage with an explicit 900 MWe power capacity.  Because the
individual reactor model doesn't have any way to start a reactor mid-cycle,
this was done to avoid having all initial LWRs refuel at the same time.  The
parameters for each case were also selected to keep capacity factors for
individual reactors very roughly around 90\%.

Instead of annual deployments, a longer 21-month deployment period is used
because it provides better natural staggering for the reactor refueling
cycles. The same deployment schedule is used for all four cases; power
capacity is built along a curve starting at 100GWe in year zero following the
1\% exponential growth curve.  This particular deployment schedule is chosen
because it causes significant fuel shortages providing interesting features to
investigate and compare.

All input files and other assets used in the analysis for each of the four
cases are publicly available for download and use \cite{Carlsen2015}.
